### 2019-03-22 _publications/jors/paper.tex
Update for tphd and guyer reviews

An online portal provides a valuable space for scientific communities
to summarize a shared challenge, collect attempts at a solution, and
present a quantitative comparison of past attempts in a compelling
way. An exemplar of such a portal is
$\mu$MAG~\cite{mumag}~\footnote{Certain commercial equipment,
  instruments, or materials (or suppliers, or software, ...) are
  identified in this paper to foster understanding. Such
  identification does not imply recommendation or endorsement by the
  National Institute of Standards and Technology, nor does it imply
  that the materials or equipment identified are necessarily the best
  available for the purpose.\label{disclaimer}}. The reusable PFHub
framework leverages existing online services to build a static portal
website that is considerably easier to deploy and maintain without
sacrificing content or scope. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.

@@

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (\emph{e.g.}, MOOSE~\cite{moose},
PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
MMSP~\cite{mmsp}~\textsuperscript{\ref{disclaimer}}) available for
solving the wide variety of phenomena associated with the PFM
(\emph{e.g.}, dendritic growth, spinodal decomposition, grain
growth). However, phase-field research groups often develop codes in
isolation and do not support or distribute the code bases to the wider
community. PFHub is a community effort spearheaded by the Center for
Hierarchical Materials Design at Northwestern University and the
National Institute of Standards and Technology to support the
development of phase-field codes. In particular, the PFHub effort
focuses on improving cross-collaboration between phase-field code
developers and practitioners by providing a standardized set of
benchmark problems~\cite{bm1, bm2} along with a web framework for
uploading and comparing benchmark results from different codes.

@@

\begin{itemize}
  \item The users are first required to upload simulation outputs to
    an archival resource (\emph{e.g.}, Figshare) configured with
    permissive cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a temporary version of the proposed website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}

A combination of Jekyll templates and Coffeescript are used to access
and download the data links in the submitted YAML files and then
display the data in interactive plots on the website.  Previous
iterations of PFHub used the Vega JSON Library~\cite{vega} to generate
the interactive plots, but now the Plotly JavaScript Graphing
Library~\cite{plotly} is used exclusively as it provides a more
programmable interface and requires less upfront configuration.

The benchmark specifications consist of equations, narrative, plots
and code samples; and are composed in Jupyter Notbooks. The Jupyter
Notebooks are included as static objects in the website after
translation into HTML using the nbconvert tool~\cite{jupyter}.

>>>>

An online portal provides a valuable space for scientific communities
to summarize a shared challenge, collect attempts at a solution, and
present a quantitative comparison of past attempts in a compelling
way. An exemplar of such a portal is
$\mu$MAG~\cite{mumag}. The reusable PFHub
framework leverages existing online services to build a static portal
website that is considerably easier to deploy and maintain without
sacrificing content or scope. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.

%% ~\footnote{Certain commercial equipment,
%%   instruments, or materials (or suppliers, or software, ...) are
%%   identified in this paper to foster understanding. Such
%%   identification does not imply recommendation or endorsement by the
%%   National Institute of Standards and Technology, nor does it imply
%%   that the materials or equipment identified are necessarily the best
%%   available for the purpose.\label{disclaimer}}

%% ~\textsuperscript{\ref{disclaimer}}

@@

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (\emph{e.g.}, MOOSE~\cite{moose},
PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
MMSP~\cite{mmsp}) available for
solving the wide variety of mesoscale phenomena (\emph{e.g.},
dendritic growth, spinodal decomposition, grain growth). However,
phase-field research groups often develop codes in isolation and do
not support or distribute the code bases to the wider community. PFHub
is a community effort spearheaded by the Center for Hierarchical
Materials Design at Northwestern University and the National Institute
of Standards and Technology to support the development of phase-field
codes. In particular, the PFHub effort focuses on improving
cross-collaboration between phase-field code developers and
practitioners by providing a standardized set of benchmark
problems~\cite{bm1, bm2} along with a web framework for uploading and
comparing benchmark results from different codes.

@@

\begin{itemize}
  \item The users are first required to upload simulation outputs to
    an archival resource (\emph{e.g.}, Figshare~\footnote{Certain
      commercial equipment, instruments, or materials (or suppliers,
      or software, ...) are identified in this paper to foster
      understanding. Such identification does not imply recommendation
      or endorsement by the National Institute of Standards and
      Technology, nor does it imply that the materials or equipment
      identified are necessarily the best available for the
      purpose.\label{disclaimer}}) configured with permissive
    cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a temporary version of the proposed website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}

A combination of Jekyll templates and Coffeescript are used to access
and download the data links in the submitted YAML files and then
display the data in interactive plots on the website. The interactive
plots are displayed using the Plotly JavaScript Graphing
Library~\cite{plotly} as it provides a programmable interface and
requires minimal configuration.

The benchmark specifications consist of equations, narrative, plots
and code samples, and are composed in Jupyter Notebooks. The Jupyter
Notebooks are included as static objects in the website after
translation into HTML using the nbconvert tool~\cite{jupyter}.
